\section{The Query-Based Pricing Framework}
\label{sec:framework}

In this section, we present the framework of query-based pricing proposed by \cite{deep2016design} , and then formally describe the pricing problems we tackle.

\subsection{Query-Based Pricing Basics}

The {\em data seller} wants to sell a database instance $\db$ through a data market, which functions as the broker. \textcolor{red}{The instance has a fixed relational schema $\bR = (R_1, \dots, R_k)$ with $k$ relations.} We denote by $\mI$ the set of possible database instances. The set $\mI$ encodes information about the data that is provided by the data seller, and is public information known to any buyer (together with the schema). We allow the set $\mI$ to be infinite, but countable. \textcolor{red}{For example, suppose that the schema consists of a single binary relation $R(A,B)$, and the domain of both attributes is $[n] = \set{1, \dots, n}$. Then, $\mI = 2^{[n] \times [n]}$, \ie the set of all directed graphs on the vertex set $[n]$.}

{\em Data buyers} can purchase information from the dataset by issuing queries in the form of a {\em query bundle}  $\bQ=\qb{Q_1, \hdots, Q_n}$, which is a vector of queries. For our purposes, a query $Q$ is a deterministic function that takes as input a database instance $\db$ and returns an output $Q(\db)$. We denote the output of the query bundle by $\bQ(\db) = \qb{Q_1(\db), \hdots Q_n(\db)}$. 

\begin{example}
	\textit{Consider a database that consists of a single \textsc{User} relation as shown in Figure~\ref{fig:example}. Suppose that the data seller has fixed the price of the entire relation to $\$100$. Consider a data buyer, Alice, who is a data analyst and wants to study user demographics. Since Alice has a limited budget, she cannot afford to purchase the entire database. Thus, Alice will extract information from the table by issuing relational queries over time. We will use this as a running example throughout the section.}
\end{example}

\begin{figure}[t]
	\centering
			\begin{tabular} {|l|l|c|c|}
				\multicolumn{4}{ l }{\textsc{User}} \\ 
				\hline
				\textsf{\underline{uid}} & \textsf{name} & \textsf{gender} & \textsf{age}  \\ \hline
				1 & Abe &  m & 18 \\ 
				2 & Alice  & f & 20 \\
				3 & Bob & m & 25 \\
				4 & Cathy & f & 22 \\
				\hline
			\end{tabular}
			\caption{\textsc{User} relation with $4$ attributes. \textsf{\underline{uid}} is the primary key.}
			\label{fig:example}
\end{figure}

A {\em pricing function} $p(\bQ, \db)$ takes as input a query bundle $\bQ$ and a database instance $\db \in \mI$ and assigns to it a price,\footnote{Observe that allowing prices to be general functions of query bundles, rather than just additive over queries allows for more expressivity and therefore more revenue for the seller.} which is a number in $ \mathbb{R}_+$. 
% The reason we consider query bundles in our setting is that in practice a data buyer will issue over time a sequence $\bQ_1, \dots, \bQ_m$ of query bundles on the database. In this case, after issuing the first $i$ queries, the data buyer should not be charged a price of $\sum_i p(\bQ_i,D)$, but instead $p(\bQ_1, \dots, \bQ_i, D)$. 

Assigning prices to query bundles without any restrictions can lead to arbitrage opportunities where a buyer misreports the query bundle he is interested in purchasing. Arbitrage can occur in the following two ways, or as a combination of the two:
%There are two different conditions where arbitrage may occur:

\introparagraph{Information Arbitrage} The first condition captures the intuition that if a query bundle $\bQ_1$ reveals a subset of information of what a query bundle $\bQ_2$ reveals, then the price of $\bQ_1$ must be no more than the price of $\bQ_2$. If this condition is not satisfied, it creates an arbitrage opportunity, since a data buyer can purchase $\bQ_2$ instead, and use it to obtain the answer of $\bQ_1$ for a cheaper price. 

Formally, we say that $\bQ_2$ determines $\bQ_1$ under database $\db$, denoted $\db \vdash \bQ_2 \dtr \bQ_1$ if for every database $\db' \in \mI$ such that $\bQ_2(\db) = \bQ_2(\db')$, we also have  $\bQ_1(\db') = \bQ_1(\db)$.
We say that the pricing function $p$ has no {\em information arbitrage} if for every database $\db \in \mI$ such that $\db \vdash \bQ_2 \dtr \bQ_1$, we have $p(\bQ_2, \db) \geq  p(\bQ_1, \db)$.

\begin{example}
	\textit{In our running example, suppose that Alice wants to count the number of female users in the relation. She can issue the query $Q_1 = \texttt{SELECT count(*) FROM User WHERE gender = 'f'}$. However, a different way she can learn the same information is by issuing the query $Q_2 = \texttt{SELECT gender,}$ $\texttt{ count(*) FROM User GROUP BY gender}$. $Q_2$ will return the number of users for each gender as its output. Suppose that the buyer charges $p(Q_1) = \$10$ and $p(Q_2) = \$5$, then there exists an information arbitrage opportunity. Since Alice can learn the required information from $Q_2$ at a {\emph{cheaper}} cost, she has no incentive to purchase $Q_1$. Thus, if the seller wants to prevent this arbitrage, he needs to ensure that $p(Q_1) \leq p(Q_2)$. Thus, the seller now sets the price of $Q_2$ to $\$10$, i.e, $p(Q_2) = \$10$.}
\end{example}

\introparagraph{Bundle Arbitrage} The second condition regards the scenario where a data buyer wants to obtain the answer for the query bundle $\bQ = \bQ_1\Vert \bQ_2$, where $\Vert$ denotes vector concatenation. Instead of asking $\bQ$ as one, the buyer can create two separate accounts, and use one to ask for $\bQ_1$ and the other to ask for $\bQ_2$. To avoid such an arbitrage situation, we must make sure that the price of $\bQ$ is at most the sum of the prices for $\bQ_1$ and  $\bQ_2$. 
%
Formally, we say that the price function $p$ has no {\em bundle arbitrage} if for every database $\db \in \mI$, we have $p(\bQ_1\Vert \bQ_2, \db) \leq p(\bQ_1, \db) + p(\bQ_2, \db)$. 


\begin{example}
	\textit{Suppose Alice now wants to find the average age of female users in the relation. She can issue the query $Q_4 = \texttt{SELECT AVG(age) FROM User WHERE gender = 'f'}$. Suppose the seller decides to price $p(Q_4) = \$20$. However, Alice could have also chosen to ask $Q_5 = \texttt{SELECT SUM(age) FROM User}$ $\texttt{ WHERE gender = 'f'}$. Now, she can obtain her desired result by combining the answers of $Q_5$ and $Q_2$ \footnote{We assume that it is public information that gender in this relation takes only two values: \textsf{m} and \textsf{f} }. If the seller prices $p(Q_5) = \$5$, then there exists a bundle arbitrage opportunity, since $p(Q_4) > p(Q_5) + p(Q_2)$ which gives Alice an incentive to split her query. To avoid this, the seller needs to ensure that $p(Q_4) \leq p(Q_5) + p(Q_2)$.}
\end{example}


\textcolor{red}{Perhaps switch around the order of the two conditions.}

We say that the pricing function $p$ is {\em arbitrage-free} if it has no information arbitrage and no bundle arbitrage. 

\subsection{From Pricing Queries to Pricing Bundles}

\textcolor{red}{Since we don't really investigate how performance changes as we change the set $S$, perhaps simplify this section by defining everything over the entire set $I$. It doesn't cost us any generality in pricing.}
In general, computing whether $\bQ_2$ determines $\bQ_1$ under some database $\db$ is an intractable problem. To overcome this obstacle, we take a different view of a query bundle. Let 
$\mS \subseteq \mI$ be any subset of $\mI$, called the {\em support set}, and define the {\em conflict set} of $\bQ$ w.r.t. to $\mS$ as:
%
\begin{align*}
\dagr{\mS}{\bQ,\db}  &= \setof{\db' \in \mS}{\bQ(\db) \neq \bQ(\db')}. 
\end{align*}

Intuitively, the conflict set contains all the database instances from $\mS$ for which the buyer knows that cannot be the underlying instance $\db$ once she learns the answer $\bQ(\db)$. This construction maps each query to the {\em  bundle} $\dagr{\mS}{\bQ,\db} $ over the common itemset $\mS$. We should remark here that the task of computing the bundle $\dagr{\mS}{\bQ,\db} $ is computationally feasible if we choose $\mS$ to be small enough, since we can simply iterate through all the items $\db' \in \mS$, and for each item check the condition 
$\bQ(\db) \neq \bQ(\db')$.

We can now compute a price for $\bQ$ by applying a set function $f: 2^{\mS} \rightarrow  \mathbb{R}_+$ on $\dagr{\mS}{\bQ, \db}$. 
\hlrone{A set function $f$ is {\em monotone} if for sets $A \subseteq B$ we always have $f(A) \leq f(B)$, and {\em subadditive} if for every set $A,B$ we have $f(A) + f(B) \geq f(A \cup B)$.}
By choosing $f$ to be monotone and subadditive, we can guarantee that the pricing function is arbitrage-free.

\begin{theorem}[\cite{deep2016design}] \label{cor:arbitrage}
Let $\mS \subseteq \mI$, and $f$ be a set function $f: 2^{\mS} \rightarrow  \mathbb{R}_+$. Then, the function $p(\bQ, \db) = f(\dagr{\mS}{\bQ, \db})$ is arbitrage-free
if and only if  $f$ is monotone and subadditive. 
\end{theorem}

\subsection{Revenue Maximization}

We consider the unlimited supply setting, where the data seller can sell any number of units of each query. 
Additionally, we assume that the buyers are single-minded: each buyer is interested in buying only a single query bundle $\bQ$; the buyer will purchase $\bQ$ only if the price $p(\bQ, \db) \leq v_\bQ$, where $v_\bQ$ is the valuation  that the buyer has for $\bQ$. 

\textcolor{red}{Again, drop $S$ and continue with $I$?}
The problem setup is as follows. We are given as input a set of $m$ buyers, where each buyer $i$ is interested of purchasing a query bundle $\bQ_i$ with valuation $v_i$. We pick a support set $\mS \subseteq \mI$ of size $n = |\mS|$. By using the transformation of queries to bundles over $\mS$, we can construct a hypergraph $\mH = (\mV,\mE)$, with vertex set $\mV = \mS$, and hyperedges $\mE = \setof{e_i}{i =1, \dots, m}$, where $e_i =\dagr{\mS}{\bQ_i, \db}$. A pricing function $p$ is a set function that maps subsets of $S$ to prices in $\mathbb{R}_+$. \footnote{Here we have overloaded $p$ to also be a pricing function with input a bundle of items.} The task at hand is to find a pricing function $p$ that is monotone and subadditive and maximizes the seller's revenue. The revenue of a pricing function $p$ is given by:
\[R(p) = \sum_{i: v_i\ge p(e_i)} p(e_i)\]
The optimal revenue is:
\[\textsc{OPT} = \max_{\text{montone; subadditive } p} R(p)\]
Many of the approximation results in the literature use a simpler upper bound on $\textsc{OPT}$, namely the sum of all bundle values $\sum_i v_i$, as a basis of comparison for algorithms' performance. Observe that this is also the maximum social welfare achievable in this setting.

\subsection{Simple Pricing Functions}

For practical applications (e.g., \textsc{Qirana}~\cite{deep2017qirana}), we must only consider functions that can be both concisely represented and also efficiently computable. For example, it is not desirable to come up with a function $p$ where we need to explicitly store all the $2^n$ values for all input bundles from $\mS$.
For this reason, we focus on a few important subclasses of monotone and subadditive set functions:
%
\begin{packed_item}
\item The {\em uniform bundle price}  $p^b(\cdot)$ assigns the same price to every hyperedge, \ie $p^b(e) = P$ for some number $P \geq 0$.
%
\item The {\em additive price} $p^a(\cdot)$ assigns a weight $w_j \geq 0$ to every item $j \in \mS$, and then defines
$p^a(e) = \sum_{j \in e} w_j$. Such a pricing function is also commonly known as an {\em item pricing}.
%
\item The {\em XOS price} $p^x(\cdot)$ defines $k$ weights $w_j^1, w_j^2, \dots, w_j^k$ for each item $j \in \mS$, and then sets the price to $p^x(e) = \max_{i=1}^k \sum_{j \in e} w_j^i$.
\end{packed_item}

Given the above three subclasses of pricing functions, we consider the following two questions, both from a theoretical and practical point of view.
First, how much do we lose in terms of revenue by replacing the optimal monotone and subadditive pricing function with a uniform, additive or XOS pricing function? In other words, we seek to understand what is the revenue we lose for the sake of computational efficiency.
Second, we want to develop algorithms that can optimize the prices for each subclass and achieve a good approximation ratio with respect to the optimal revenue.


